curiobaby_drop model analysis

### 2021-01-23 analysis/model_analysis_v2.Rmd
added new features

save(mdat, file=here("models/model_data.RData"))
```

@@

knitr::kable(fit_tab, digits = 2)
```

@@

```{r, eval=F}
fits %>% ggplot(aes(x=beta, y=mse, color=AgeGroup)) +
  #geom_text(aes(label=feature)) + 
  geom_point() +
  theme_minimal()
```
So generally, children's choices are best explained by small values of beta (.5, the minimum tested).

>>>>

@@

knitr::kable(fit_tab, digits = 3)
```

@@

```{r, eval=F}
fits %>% ggplot(aes(x=beta, y=mse, color=AgeGroup)) +
  #geom_text(aes(label=feature)) + 
  geom_point(alpha=.5) +
  theme_minimal()
```
So generally, children's choices are best explained by small values of beta (.5, the minimum tested).
